---
title: "assignment 2"
output:
  pdf_document: default
  word_document: default
  html_document: default
date: "2023-10-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
options(repos = c(CRAN = "https://cran.rstudio.com"))
```

\#**Install and Load the dplyr Package**

```{r}
install.packages("dplyr")
```

```{r}
library(dplyr)
```

#clear the environment

```{r}
rm(list = ls())
```

#load the dataset

```{r}
d<-read.csv("vdem_1984_2022_external.csv")
```

#1. code-book lookup

#1) According to the vdem code-book, indicators related to education are "8.1.1 Education 15+ (E) (e_peaveduc)" and "8.1.2 Educational inequality, Gini (E) (e_peedgini)".

#2) For "Education 15+ (E) (e_peaveduc)", datas are available from 1820-2021. And for "Educational inequality, Gini (E) (e_peedgini)", datas are available from 1850-2010. But in the dataset of "vdem_1984_2022_external.csv" we only have data from 1984. And we can know the countries and years in this dataset by running this code shown below.

#Countries and years in the dataset

```{r}
d |> select(country_name, year) |> distinct()
```

#3). According to the code-book there are many sources, such as Clio-Infra (2018), 'Clio-Infra Project (Database)'.**URL:** <http://www.clio-infra.eu/> etc.

#2. subset by columns

#1) dataset with country, year and indicators of education quality

```{r}
d_edu<-d|>
  select(country_name, year, e_peaveduc, e_peedgini)

d_edu
```

#2) rename

```{r}
d_edu <-d_edu |>
  rename("Years_of_education"="e_peaveduc", "Educational_inequality"="e_peedgini")

d_edu
```

#3. Subset by rows

#1) Want countries-years with the highest education level.

```{r}
d_edu|>
  slice_max(order_by =Years_of_education, n=5)
```

#2) Want countries-years with greatest gini-coefficient

```{r}
d_edu|>
  slice_max(order_by =Educational_inequality, n=5)
```

#4. summarize

#1) check data availability:

#number of data "Years_of_education" missing for each country

```{r}
d_edu|>
  mutate(Years_of_education_missing=as.numeric(is.na(Years_of_education)), .after = Years_of_education)|>
  group_by(country_name)|>
  summarise(N_Years_of_education_missing=sum(Years_of_education_missing))
```

#number of data "Educational_inequality" missing for each country

```{r}
d_edu|>
  mutate(Educational_inequality_missing=as.numeric(is.na(Educational_inequality)), .after = Educational_inequality)|>
  group_by(country_name)|>
  summarise(N_Educational_inequality_missing=sum(Educational_inequality_missing))
```

#number of data "Years_of_education" missing for each year

```{r}
d_edu|>
  mutate(Years_of_education_missing=as.numeric(is.na(Years_of_education)), .after = Years_of_education)|>
  group_by(year)|>
  summarise(N_Years_of_education_missing=sum(Years_of_education_missing))
```

#number of data "Educational_inequality" missing for each year

```{r}
d_edu|>
  mutate(Educational_inequality_missing=as.numeric(is.na(Educational_inequality)), .after = Educational_inequality)|>
  group_by(year)|>
  summarise(N_Educational_inequality_missing=sum(Educational_inequality_missing))
```

#2) 1) Average level of education quality 1984-2022

```{r}
d_edu|>
  filter(year>=1984 & year<=2022)|>
  group_by(country_name)|>
  summarise(Years_of_education_average=mean(Years_of_education, na.rm = TRUE),
            Educational_inequality_average=mean(Educational_inequality, na.rm = TRUE))
```

#2) 2) Change of education quality 1984-2022

```{r}
d_edu|>
  filter(year>=1984 & year<=2022)|>
  group_by(country_name)|>
  summarise(
    Years_of_education_growth_2022_1984 = last(Years_of_education) - first(Years_of_education),
    Educational_inequality_decrease_2022_1984 = last(Educational_inequality) - first(Educational_inequality))|>
  arrange(-Years_of_education_growth_2022_1984)
```

#3) Best: Botswana, worst: Tajikistan.
